Confirmation of \srcfull{} as a long period radio transient

### 2025-06-06 paper/main.tex
More tweaks to papers and figures

% Abstract of the paper
\begin{abstract}
We report the discovery of several new pulses from the source \srcfull{} (\src{}), originally identified from a single 2-min long pulse, confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours. The pulses are significantly scattered, consistent with Galactic electron density models. Two of the new pulses also had measurable polarisation, but unlike the originally detected pulse, the polarisation angle does not behave as expected from the rotating vector model. We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes. We conjecture that, like other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars.
\end{abstract}

@@

Following its re-detection in the ASKAP data, follow-up observations were conducted at L/S band with the ATCA telescope under the project code C3363 (P.I: Tara Murphy). \src\ was observed once on 2024-10-04, for a total of 1.5\,hrs, and again on 2024-10-12, for a total of 2.4\,hrs. At the beginning of each observation, 1934$-$638 was used to calibrate the bandpass, and during the observations, 1748$-$253 was used as a phase calibrator. Data were flagged, calibrated, and imaged using standard recipes from the Common Astronomy Software Applications package \citep[CASA;][]{casa}. The resulting sky model was subtracted from the visibilities (excluding the source of interest). These model-subtracted visibilities were phase-centered on the \src{} and averaged over the baselines to produce the dynamic spectra.

We identified two faint pulses (4--5 $\sigma$; see Table~\ref{tbl:toas}) in the observation taken on 2024-10-04. However, observations taken on 2024-10-12 did not yield any pulses (at 3-$\sigma$ level). We inspected the data around the expected time of arrival (using Equation~\ref{eqn:timing}) but did not find any pulses. The instantaneous noise level around the expected time of arrivals is close to 1\,mJy. If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 can be sufficient to explain the detection of pulse on 2024-10-04 and the absence of pulses on 2024-10-12, given that the source is faint at higher frequencies.

>>>>

% Abstract of the paper
\begin{abstract}
We report the discovery of several new pulses from the source \srcfull{} (\src{}), originally identified from a single 2-min long pulse, confirming it as a long period transient (LPT) with a period of ${\sim}1.16\,$hours. The pulses are significantly scattered, consistent with Galactic electron density models. Two of the new pulses also had measurable polarisation, but unlike the originally detected pulse, the polarisation angle does not behave as expected from the rotating vector model. We interpret historical non-detections of \src{} as an intrinsic intermittency that occurs on month-long timescales, and discuss possible causes. We conjecture that, like some other LPTs with periods $\gtrsim 1\,$hour, \src{} is a white-dwarf binary pulsar, but note that its period is marginally shorter than the minimum known orbital period for the class of cataclysmic variables known as polars.
\end{abstract}

@@

Following its re-detection in the ASKAP data, follow-up observations were conducted at L/S bands with the ATCA telescope under the project code C3363 (P.I: Tara Murphy). \src\ was observed once on 2024-10-04, for a total of 1.5\,hrs, and again on 2024-10-12, for a total of 2.4\,hrs. At the beginning of each observation, 1934$-$638 was used to calibrate the bandpass, and during the observations, 1748$-$253 was used as a phase calibrator. Data were flagged, calibrated, and imaged using standard recipes from the Common Astronomy Software Applications package \citep[CASA;][]{casa}. The resulting sky model was subtracted from the visibilities (excluding the source of interest). These model-subtracted visibilities were phase-centered on the \src{} and averaged over the baselines to produce the dynamic spectra.

We identified two faint pulses (4--5 $\sigma$; see Table~\ref{tbl:toas}) in the observation taken on 2024-10-04. However, observations taken on 2024-10-12 did not yield any pulses (at 3-$\sigma$ level). We inspected the data around the expected time of arrival (using Equation~\ref{eqn:timing}) but did not find any pulses. The instantaneous noise level, per 10\,s integration time bin, around the expected time of arrivals is close to 1\,mJy. If pulse-to-pulse flux density variations, similar to ones observed in MWA data (Table~\ref{tbl:toas}), also occur at L/S band, then even a factor 1.5--2 variation can be sufficient to explain the detection of pulses on 2024-10-04 and the absence of pulses on 2024-10-12, given that the source is faint at higher frequencies.
